The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Update slides

---
title: "The Rapid Cycleway Prioritisation Tool"
subtitle: "`r emojifont::emoji('rocket')`<br/>methods and results"
author: "Robin Lovelace and Joey Talbot"
institute: "University of Leeds, [Institute for Transport Studies](https://environment.leeds.ac.uk/transport)"
date: "Green Transport Recovery Series, 2020-06-17"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts]
    lib_dir: libs
    nature: 
      beforeInit: "https://platform.twitter.com/widgets.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

```{r, echo=FALSE}
knitr::include_graphics("https://pbs.twimg.com/media/EToi6UVXQAEmY2h?format=jpg&name=large")
```

<!-- 14h30-15h30 lecture part (this could already drift towards the practical part but doesn't have to ...) -->

<!-- 15:30-16h00 coffee break -->

<!-- 16h00-17h00 hands-on workshop (could be somewhat open-ended, we'll have the room all afternoon - but if we would go into extra time, we should make a short 'cut' around 17h such that those who have/want to go home can do so). -->

<!-- Sally: see it as an opportunity - vital for change -->

<!-- Lucy: Propensity to cycle tool -->

<!-- It's brilliant, magic, helps imagine what the future could be like -->

background-image: url(https://pbs.twimg.com/media/EZvQNJlWoAE4D_c?format=jpg&name=4096x4096)

@@

### How to cope with reduced public transport capacity post COVID-19?

@@

## Spatial networks can support planning

### Transport networks are spatial networks

Spatial network representation in R:

@@

### sf + igraph used in project to support investment in 'pop-ups' nationwide

@@

@@

Free and open results:

[www.cyipt.bike/rapid](https://www.cyipt.bike/rapid)

Source code: [github.com/cyipt/popupCycleways](https://github.com/cyipt/popupCycleways)

<!-- ![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/facet-output.png) -->

```{r, out.width="70%", echo=FALSE}
# knitr::include_graphics("https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/facet-output.png")
```

@@

## Ingredients to prioritise transport infrastructure

- Current travel patterns
- Road attribute data 
- Potential usage levels
- Impact on overall network

**Spatial networks can help, especially with the last two**

Source: https://www.pct.bike/

![](figs/pct.png)

>>>>

---
title: "The Rapid Cycleway Prioritisation Tool"
subtitle: "🛣🚲🚀<br/>methods and results<br/>[cyipt.bike/rapid](https://www.cyipt.bike/rapid/)"
author: "Robin Lovelace and Joey Talbot"
institute: "University of Leeds, [Institute for Transport Studies](https://environment.leeds.ac.uk/transport). [Source code](https://github.com/cyipt/popupCycleways/blob/master/rapid-slides.Rmd)."
date: "Green Transport Recovery Series, 2020-06-17"
output:
  xaringan::moon_reader:
    css: [default, robot, robot-fonts]
    lib_dir: libs
    nature: 
      beforeInit: "https://platform.twitter.com/widgets.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

@@

background-image: url(https://pbs.twimg.com/media/EZvQNJlWoAE4D_c?format=jpg&name=4096x4096)
background-position: bottom
background-size: contain

@@

# How does the tool identify ‘top ranked new cycleways’?

@@

# How does the tool identify what a ‘cohesive network’ might look like?

# How can I find the results for my area?

# How should I use these results?

@@

@@

## Results

# Case study: Leeds

@@

See the results at:

[www.cyipt.bike/rapid/west-yorkshire](https://www.cyipt.bike/rapid/west-yorkshire)

@@

## What are the key limitations of the tool?

## Where can I find further information about the tool?

## How to cope with reduced public transport capacity post COVID-19?
